Contextual Combinatorial Cascading Bandits

### 2016-01-17 contextual combinatorial cascading bandits.tex
update problem formulation-general case

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

@@

      \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
      \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
      \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}

>>>>

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

\section{Problem Formulation-general case}

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent; the feature vectors combine both the information of the user and the corresponding base arm. \shengyu{Add a standard/typical example (just one sentence) to illustrate the combination?} For example, suppose the user at time $t$ is represented by the feature vector $u_t$ and the feature vector of the base arm $a$ is $v_a$, then we can let $x_{t,a}$ be $(u_t, v_a)$ which combines both the information of the user and the base arm. \shuai{I have added one sentence.} Then the learning agent recommends a feasible action $\bA_t=\{ \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t \} \in \cS$ to the user and notice that the size of the action is not fixed. Then according to the user behavior and the structure of the action $\bA_t$, we observe the weights of fist $\bO_t$ base arms in $\bA_t$. For example in website recommender systems, if the user checks from the first recommended website and stops when she finds one interesting or has checked all websites, then the observed base arms are checked websites.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
  % \label{eq:expectation}
  \EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$.

We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$. At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

We consider the position discount. For example in recommender systems, the positions to display advertisements might have difference prices, hence of different value when user clicks on it.

The reward function on round $t$ is an application dependent function. We assume the expected reward function $f(A, w)$ of an action $A$ with expected weights $w$ satisfy the following assumptions.

Monotonicity The expected reward $f(A, w)$ is a non-decreasing with respect to $w$. For any $d$ dimension vectors $w$ and $w'$, if $w(i) \leq w'(i)$, we have $f(A, w) \leq f(A, w')$.

Lipschitz continuity The expected reward function f(A, w) is a Lipschitz continuous with respect to $w$ together with position discount $\gamma$. In particular, there is a constant $B>0$ such that, for any $w$ and $w'$, we have
$$
	|f(A, w) - f(A, w')| \leq B\sqrt{\sum_{i \in Ind(A)} \gamma_i^2(w(i) - w'(i))^2}
$$

We don't require the agent knows how the function $f(A, w)$ is defined. We only assume the agent has access to an oracle $\cO(A, w)$. More precisely, an oracle $\cO(\cS, w)$ is  called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if given input $w$ and $\cS$, the oracle always returns an action(super arm) $A = \cO(r, \cS) \in \cS$ satisfying $f(w, S) \geq \alpha opt_{w, \cS}$ where $opt_{w, \cS} = \max_{s \in \cS}$ f(r, S).

The $\alpha$-regret on time $t$ can be written as
$$
R_t = \alpha opt_{w_t} - f(w_t, A_t).
$$
Our goal is to minimize the cumulative regret $R = \sum_{t=1}^n R_t$.

@@

      \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \cO_{\cS}(\bU_t)$ } 
      \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
      \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
